Supporting Information : Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-04-03 SuppMat.Rmd
add guidelines for intro and results
modified documentation

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
set.seed(seed)
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231659,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a_pennycuick,b_pennycuick),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

>>>>

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("bifurcation_pennycuick.R"))}
set.seed(seed)
source("./bifurcation_pennycuick.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231659,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a_pennycuick,b_pennycuick),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}
